Value Ordering, Discrepancies, and Restarts for Subgraph Algorithms\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/026842/1 and EP/M508056/1]}

### 2017-12-14 paper/paper.tex
More thingies

The subgraph isomorphism problem is to find a copy of a small ``pattern'' graph inside a larger
``target'' graph.  The current single strongest subgraph isomorphism solver uses ``highest degree
first'' as a value-ordering heuristic to direct a constraint programming style search
\citep{DBLP:conf/cp/McCreeshP15,DBLP:conf/lion/KotthoffMS16,DBLP:conf/ijcai/McCreeshPT16}.  This is
much better than not having a value-ordering heuristic at all, but it is far from perfect,
particularly for early branching choices. There are two reasons to suspect a better option may
possible.  Firstly, even if degree were a perfect source of information, many target graphs do not
have a large degree distribution, and so we would still need to determine \emph{which} vertex of
highest degree would be best.  Secondly, experiments with a parallel search strategy which
explicitly steals early branching choices often gives strongly super-linear speedups on satisfiable
instances \citep{DBLP:conf/cp/McCreeshP15}.

@@

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-mcsplit.pdf}
    \caption{McSplit speedups}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-kdown.pdf}
    \caption{k${\downarrow}$ speedups}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-mcs.pdf}
    \caption{k${\downarrow}$ and McSplit cumulative curves.}
\end{figure}

@@

@@

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-as.pdf}
    \caption{?? Aggregate speedups on satisfiable instances}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-scatter-degree.pdf}

@@

\bibliographystyle{named}
\bibliography{dblp}

>>>>

The subgraph isomorphism problem is to find a copy of a small ``pattern'' graph inside a larger
``target'' graph.  The current single strongest subgraph isomorphism solver uses ``highest degree
first'' as a value-ordering heuristic to direct a constraint programming style search
\citep{DBLP:conf/cp/McCreeshP15,DBLP:conf/lion/KotthoffMS16,DBLP:conf/ijcai/McCreeshPT16}. This
heuristic is far from perfect. Furthermore, even if degree were a perfect source of information,
many target graphs do not have a large degree distribution, so we would still need to determine
\emph{which} vertex of highest degree would be best.

@@

?? Two recent maximum common induced subgraph algorithms: k${\downarrow}$
\citep{DBLP:conf/aaai/HoffmannMR17}, and McSplit \citep{DBLP:conf/ijcai/McCreeshPT17}. The former
attempts to solve the problem by first trying to solve the induced subgraph isomorphism problem, and
then if that fails, retries allowing a single unmatched vertex (and thus using weaker invariants),
and so on. Due to its similarity to \cref{algorithm:sip}, we can introduce the same bias and restart
strategy.

The McSplit algorithm, meanwhile, uses a constraint programming style search, but with special
propagators and backtrackable data structures that exploit special properties of the problem. The
unconventional domain store used by McSplit precludes the use of arbitrary unit propagation, and so
when introducing restarts, we cannot propagate using nogoods. Instead, we can only detect when we
are inside an already-visited branch. We must therefore use the one watched literal scheme instead.

?? Benchmark results on the same families of instances are shown in
\cref{figure:mcsplit,figure:kdown,figure:mcs}. Clearly beneficial. Note that on McSplit we're doing
extra work and this shows, but it's still worthwhile.

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-mcsplit.pdf}
    \caption{McSplit speedups ?? partial data}\label{figure:mcsplit}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-kdown.pdf}
    \caption{k${\downarrow}$ speedups ?? missing data}\label{figure:kdown}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-mcs.pdf}
    \caption{k${\downarrow}$ and McSplit cumulative curves ?? partial and missing
    data}\label{figure:mcs}
\end{figure}

@@

\clearpage
\bibliographystyle{named}
\bibliography{dblp}

\clearpage
\appendix

@@

\begin{figure}[h]
    \centering
    \includegraphics*{gen-graph-as.pdf}
    \caption{?? Aggregate speedups on satisfiable instances}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics*{gen-graph-as-mcs.pdf}
    \caption{?? Aggregate speedups on MCS instances}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics*{gen-graph-scatter-degree.pdf}

@@
